Assessing the Feasibility of a Cluster Randomised Trial on the Effect of Trauma Life Support Training: A Pilot Study

### 2024-11-14 pilot-publication/manuscript.Rmd
Update manuscript

##### Johanna Berg (JB) `r insert_orcid_link("0000-0001-7553-7337")`
Department of Global Public Health, Karolinska Institutet, Stockholm, Sweden.

@@

##### Shamita Chatterjee (SC) `r insert_orcid_link("0000-0002-9460-108X")`
Department of Surgery, Institute of Post Graduate Medical Education and Research, Kolkata, India.

##### Li Felländer-Tsai (LFT) `r insert_orcid_link("0000-0003-0693-6080")`
Division of Orthopaedics and Biotechnology, Department of Clinical Science Intervention and Technology (CLINTEC), Karolinska Institutet, Stockholm, Sweden.

@@

##### Monty Khajanchi (MK)`r insert_orcid_link("0000-0002-0898-6391")`
WHO Collaboration Centre for Research in Surgical Care Delivery in LMIC, Mumbai, India.

@@

##### Catherine Juillard (CJ) `r insert_orcid_link("0000-0003-0847-8933")`
Division of General Surgery, Department of Surgery, David Geffen School of Medicine at UCLA, Los Angeles, California, United States of America.

@@

##### Rajdeep Singh (RS) `r insert_orcid_link("0000-0001-6593-2624")`
Department of Surgery, Maulana Azad Medical College, New Delhi, India.

##### Kapil Dev Soni (KDS) `r insert_orcid_link("0000-0003-1214-4119")`
Critical and Intensive Care, JPN Apex Trauma Center, All India Institute of Medical Sciences, New Delhi, India.

##### Lovisa Strömmer (LS) `r insert_orcid_link("0000-0001-5424-7111")`
Division of Surgery and Oncology, Department of Clinical Science, Intervention and Technology (CLINTEC),  and Department of Global Public Health, Karolinska Institutet, Stockholm, Sweden.

@@

##### Marie Hasselberg (MH)
Department of Global Public Health, Karolinska Institutet, Stockholm, Sweden.

@@

##### Debabrata Kundu (DK)
Department of Surgery, Medical College Kolkata, Kolkata, India.

@@

##### Arun Prasad (AP)

@@

##### Harris Solomon (HS)
Department of Cultural Anthropology and the Duke Global Health Institute, Duke University, Durham, USA.

##### Megha Tandon (MT)
Department of Surgery, Vardhman Mahavir Medical College and Safdarjung Hospital, New Delhi, India.

@@

Considering the widespread use of trauma life support training, several systematic reviews call for trials in settings where these programmes are not routinely implemented [@Mohammad2013; @Jayaraman2014; @Kadhum2020]. Our study represents the first published attempt at a controlled trial of the effect of trauma life support training och patient outcomes, and we conclude that conducting a full-scale cluster randomised trial should be feasible after incorporating the lessons of this pilot.

>>>>

##### Johanna Berg (JB) `r insert_orcid_link("0000-0001-7553-7337")` <!-- Accepted -->
Department of Global Public Health, Karolinska Institutet, Stockholm, Sweden.

@@

##### Shamita Chatterjee (SC) `r insert_orcid_link("0000-0002-9460-108X")` <!-- Accepted -->
Department of Surgery, Institute of Post Graduate Medical Education and Research, Kolkata, India.

##### Li Felländer-Tsai (LFT) `r insert_orcid_link("0000-0003-0693-6080")` <!-- Accepted -->
Division of Orthopaedics and Biotechnology, Department of Clinical Science Intervention and Technology (CLINTEC), Karolinska Institutet, Stockholm, Sweden.

@@

##### Monty Khajanchi (MK)`r insert_orcid_link("0000-0002-0898-6391")` <!-- Accepted -->
WHO Collaboration Centre for Research in Surgical Care Delivery in LMIC, Mumbai, India.

@@

##### Catherine Juillard (CJ) `r insert_orcid_link("0000-0003-0847-8933")` <!-- Accepted -->
Division of General Surgery, Department of Surgery, David Geffen School of Medicine at UCLA, Los Angeles, California, United States of America.

@@

##### Rajdeep Singh (RS) `r insert_orcid_link("0000-0001-6593-2624")` <!-- Accepted -->
Department of Surgery, Maulana Azad Medical College, New Delhi, India.

##### Kapil Dev Soni (KDS) `r insert_orcid_link("0000-0003-1214-4119")` <!-- Accepted -->
Critical and Intensive Care, JPN Apex Trauma Center, All India Institute of Medical Sciences, New Delhi, India.

##### Lovisa Strömmer (LS) `r insert_orcid_link("0000-0001-5424-7111")` <!-- Accepted -->
Division of Surgery and Oncology, Department of Clinical Science, Intervention and Technology (CLINTEC),  and Department of Global Public Health, Karolinska Institutet, Stockholm, Sweden.

@@

##### Marie Hasselberg (MH) <!-- Accepted -->
Department of Global Public Health, Karolinska Institutet, Stockholm, Sweden.

@@

##### Debabrata Kundu (DK) <!-- Accepted -->
Department of Surgery, Medical College Kolkata, Kolkata, India.

@@

##### Arun Prasad (AP) <!-- Accepted -->

@@

##### Harris Solomon (HS) <!-- Accepted -->
Department of Cultural Anthropology and the Duke Global Health Institute, Duke University, Durham, USA.

##### Megha Tandon (MT) <!-- Accepted -->
Department of Surgery, Vardhman Mahavir Medical College and Safdarjung Hospital, New Delhi, India.

@@

Considering the widespread use of trauma life support training, several systematic reviews call for trials in settings where these programmes are not routinely implemented [@Mohammad2013; @Jayaraman2014; @Kadhum2020]. Our study represents the first published attempt at a controlled trial of the effect of trauma life support training on patient outcomes, and we conclude that conducting a full-scale cluster randomised trial should be feasible after incorporating the lessons of this pilot.
